Meet the team

### 2025-01-17 index.qmd
site and layout updates

The **Action, Cognition, and Metascience Lab** is an interdisciplinary research team investigating basic scientific questions about how the human brain controls and learns skilled actions. We study decision-making for action and practice factors supporting skill acquisition and maintenance in single- and multi-agent scenarios. We also conduct metascience research to gain important insights into research practices within kinesiology and sport science. We are located in the Ivor Wynne Centre, which is home to the [Department of Kinesiology](https://www.science.mcmaster.ca/kinesiology/){target="_blank"} within the [Faculty of Science](https://www.science.mcmaster.ca/){target="_blank"} at [McMaster University](https://www.mcmaster.ca/){target="_blank"}.

>>>>

The **Action, Cognition, and Metascience Lab** is an interdisciplinary research team interested in how the human brain controls and learns skilled actions in healthy and clinical populations. We also conduct metascience research to gain insights into research practices within kinesiology and related areas. The lab is located in the Ivor Wynne Centre, which is home to the [Department of Kinesiology](https://www.science.mcmaster.ca/kinesiology/){target="_blank"} within the [Faculty of Science](https://www.science.mcmaster.ca/){target="_blank"} at [McMaster University](https://www.mcmaster.ca/){target="_blank"}.

### 2025-01-17 papers.qmd
site and layout updates

---
title: "Papers"
pagetitle: "CarterLab | Papers"
toc: true
toc-title: "Jump to..."
listing:
  - id: preprints
    contents: "papers/preprints/*.qmd"
    template: papers.ejs
    sort:
      - "year desc"
      - "author"
  - id: papers2020
    contents: "papers/2020-24/*.qmd"
    template: papers.ejs
    sort:
      - "year desc"
      - "author"
  - id: papers2015
    contents: "papers/2015-19/*.qmd"
    template: papers.ejs
    sort:
      - "year desc"
      - "author"
  - id: papers2010
    contents: "papers/2010-14/*.qmd"
    template: papers.ejs
    sort:
      - "year desc"
      - "author"
---

@@

:::{#preprints}
:::

## 2020--24

:::{#papers2020}
:::

## 2015--19

:::{#papers2015}
:::

## 2010--14

:::{#papers2010}
:::

>>>>

---
title: "Papers"
pagetitle: "CarterLab | Papers"
toc: true
toc-title: "Jump to..."
---

@@

- Calalo JA., Ngo TT., Sullivan SR., Strand K., Buggeln JH., Lokesh R., Roth AM., Carter MJ., Kurtzer IL., & Cashaback JGA. (2024). Online movements reflect ongoing deliberation. *bioR$\chi$iv*. ---
[{{< ai doi >}}](https://doi.org/10.1101/2024.08.19.608669){target="_blank" style="color: inherit;"}

- de Brouwer AJ., Carter MJ., Smail LC., Wolpert DM., Gallivan JP., & Flanagan JR. (2020). Gaze behaviour reveals flexible encoding of competing reach goals under conditions of target uncertainty. *bioR$\chi$iv*. ---
[{{< ai doi >}}](https://doi.org/10.1101/2020.09.02.279414){target="_blank" style="color: inherit;"}

## 2025

- St. Germain L., McKay B., Tandon C., Seedu J., Barbera L., Carrillo C., Brown D.M.Y., & Carter, MJ. (2025). Autonomy-supportive instructional language does not enhance skill acquisition compared to controlling instructional language. *Psychological Research*. ---
[{{< ai doi >}}](https://doi.org/10.1007/s00426-024-02059-z){target="_blank" style="color: inherit;"}
[{{< fa file-pdf >}}](https://raw.github.com/cartermaclab/carterlab-papers/main/2025_st-germain-etal_autonomy-supportive-instructional-language-does-not-enhance-skill-acquisition-compared-to-controlling-instructional-language.pdf){target="_blank" style="color: inherit;"}
[{{< fa brands github >}}](https://github.com/cartermaclab/expt_instructional-language){target="_blank" style="color: inherit;"}

## 2024

- McKay B., Corson AE., Seedu J., De Faveri CS., Hasan H., Arnold K., Adams FC., & Carter MJ. (2024). Reporting bias, not external focus: A robust Bayesian meta-analysis and systematic review of the external focus of attention literature. *Psychological Bulletin*. ---
[{{< ai doi >}}](https://doi.org/10.1037/bul0000451){target="_blank" style="color: inherit;"}
[{{< fa file-pdf >}}](https://raw.github.com/cartermaclab/carterlab-papers/main/2024_mckay-etal_reporting-bias-not-external-focus-a-robust-bayesian-meta-analysis-and-systematic-review-of-the-external-focus-of-attention.pdf){target="_blank" style="color: inherit;"}
[{{< fa brands github >}}](https://github.com/cartermaclab/proj_foa-optimal-theory){target="_blank" style="color: inherit;"}

- Roth AM., Buggeln JH., Hoh JE., Wood JM., Sullivan SR., Ngo TT., Calalo JA., Lokesh R., Morton SM., Grill S., Jeka JJ., Carter MJ., & Cashaback JGA. (2024). Roles and interplay of reinforcement-based and error-based processes during reaching and gait in neurotypical adults and individuals with Parkinson’s disease *PLoS Computational Biology*. ---
[{{< ai doi >}}](https://doi.org/10.1371/journal.pcbi.1012474){target="_blank" style="color: inherit;"}
[{{< fa file-pdf >}}](https://raw.github.com/cartermaclab/carterlab-papers/main/2024_roth-etal_roles-and-interplay-of-reinforcement-based-and-error-based-processes-during-reaching-and-gait-in-neurotypical-adults-and-indi.pdf){target="_blank" style="color: inherit;"}
[{{< fa brands github >}}](https://github.com/CashabackLab/Roles_and_Interplay_of_Reinforcement_and_Error){target="_blank" style="color: inherit;"}

- Roth AM., Lokesh R., Tang J., Buggeln JH., Smith C., Calalo JA., Sullivan SR., Ngo T., St. Germain L., Carter MJ., & Cashaback JGA. (2024). Punishment leads to greater sensorimotor learning but less movement variability compared to reward. *Neuroscience*. ---
[{{< ai doi >}}](https://doi.org/10.1016/j.neuroscience.2024.01.004){target="_blank" style="color: inherit;"}
[{{< fa file-pdf >}}](https://raw.github.com/cartermaclab/carterlab-papers/main/2024_roth-etal_punishment-leads-to-greater-sensorimotor-learning-but-less-movement-variability-compared-to-reward.pdf){target="_blank" style="color: inherit;"}

## 2023

- McKay B., Bacelar MFB., Parma JO., Miller MW., & Carter, MJ. (2023). The combination of reporting bias and underpowered study designs has substantially exaggerated the motor learning benefits of self-controlled practice and enhanced expectancies: A meta-analysis. *International Review of Sport and Exercise Psychology*. ---
[{{< ai doi >}}](https://doi.org/10.1080/1750984X.2023.2207255){target="_blank" style="color: inherit;"}
[{{< fa file-pdf >}}](https://raw.github.com/cartermaclab/carterlab-papers/main/2023_mckay-etal_the-combination-of-reporting-bias-and-underpowered-study-designs-has-substantially-exaggerated-the-motor-learning-benefits-of.pdf){target="_blank" style="color: inherit;"}
[{{< fa brands github >}}](https://github.com/cartermaclab/proj_sc-ee-optimal-theory){target="_blank" style="color: inherit;"}

- McKay B., Corson A., Vinh M., Jeyarajan G., Tandon C., Brooks H., Hubley J., & Carter MJ. (2023). Low prevalence of a priori power analyses in motor behavior research. *Journal of Motor Learning and Development*. ---
[{{< ai doi >}}](https://doi.org/10.1123/jmld.2022-0042){target="_blank" style="color: inherit;"}
[{{< fa file-pdf >}}](https://raw.github.com/cartermaclab/carterlab-papers/main/2023_mckay-etal_low-prevalence-of-a-priori-power-analyses-in-motor-behavior-research.pdf){target="_blank" style="color: inherit;"}
[{{< fa brands github >}}](https://github.com/cartermaclab/proj_power-motor-behaviour){target="_blank" style="color: inherit;"}

- McKay B., Bacelar MFB., & Carter MJ. (2023). On the reproducibility of power analyses in motor behavior research. *Journal of Motor Learning and Development*. ---
[{{< ai doi >}}](https://doi.org/10.1123/jmld.2022-0061){target="_blank" style="color: inherit;"}
[{{< fa file-pdf >}}](https://raw.github.com/cartermaclab/carterlab-papers/main/2023_mckay-etal_on-the-reproducibility-of-power-analyses-in-motor-behavior-research.pdf){target="_blank" style="color: inherit;"}
[{{< fa brands github >}}](https://github.com/cartermaclab/proj_power-reproducibility-motor-behaviour){target="_blank" style="color: inherit;"}

- Lokesh R., Sullivan SR., St. Germain L., Roth AM., Calalo JA., Buggeln J., Ngo T., Marchhart VRF., Carter MJ., & Cashaback JGA. (2023). Visual accuracy dominates over haptic speed for state estimation of a partner during collaborative sensorimotor interactions. *Journal of Neurophysiology*. ---
[{{< ai doi >}}](https://doi.org/10.1152/jn.00053.2023){target="_blank" style="color: inherit;"}
[{{< fa file-pdf >}}](https://raw.github.com/cartermaclab/carterlab-papers/main/2023_lokesh-etal_visual-accuracy-dominates-over-haptic-speed-for-state-estimation-of-a-partner-during-collaborative-sensorimotor-interactions.pdf){target="_blank" style="color: inherit;"}
[{{< fa brands github >}}](https://github.com/CashabackLab/VisionHaptics_Collab_OFCModel){target="_blank" style="color: inherit;"}

- McKay B. & Carter MJ. (2023). A critical re-analysis of six implicit learning papers. *Meta-Psychology*. ---
[{{< ai doi >}}](https://doi.org/10.15626/MP.2021.2938){target="_blank" style="color: inherit;"}
[{{< fa file-pdf >}}](https://raw.github.com/cartermaclab/carterlab-papers/main/2023_mckay-carter_a-critical-re-analysis-of-six-implicit-learning-papers.pdf){target="_blank" style="color: inherit;"}
[{{< fa brands github >}}](https://github.com/cartermaclab/comm_lola-tzetzis-data-irregularities){target="_blank" style="color: inherit;"}

- Roth AM., Calalo JA., Lokesh R., Sullivan SR., Grill S., Jeka JJ., van der Kooij K., Carter MJ., & Cashaback JGA. (2023). Reinforcement-based processes actively regulate motor exploration along redundant solution manifolds. *Proceedings of the Royal Society B*. ---
[{{< ai doi >}}](https://doi.org/10.1098/rspb.2023.1475){target="_blank" style="color: inherit;"}
[{{< fa file-pdf >}}](https://raw.github.com/cartermaclab/carterlab-papers/main/2023_roth-etal_reinforcement-based-processes-actively-regulate-motor-exploration-along-redundant-solution-manifolds.pdf){target="_blank" style="color: inherit;"}
[{{< fa brands github >}}](https://github.com/CashabackLab/Exploration-Along-Solution-Manifolds-Data){target="_blank" style="color: inherit;"}

- St. Germain L., McKay B., Poskus A., Williams A., Leshchyshen O., Feldman S., Cashaback JGA., & Carter MJ. (2023). Exercising choice over feedback schedules during practice is not advantageous for motor learning. *Psychonomic Bulletin & Review*. ---
[{{< ai doi >}}](https://doi.org/10.3758/s13423-022-02170-5){target="_blank" style="color: inherit;"}
[{{< fa file-pdf >}}](https://raw.github.com/cartermaclab/carterlab-papers/main/2023_st-germain-etal_exercising-choice-over-feedback-schedules-during-practice-is-not-advantageous-for-motor-learning.pdf){target="_blank" style="color: inherit;"}
[{{< fa brands github >}}](https://github.com/cartermaclab/expt_sc-feedback-characteristics){target="_blank" style="color: inherit;"}

## 2022

*Note. Parental leave May 2022 to Dec 2022*

- McKay B., Yantha ZD., Hussein J., Carter MJ., Ste-Marie DM. (2022). Meta-analytic findings of the self-controlled motor learning literature: Underpowered, biased, and lacking evidential value. *Meta-Psychology*. ---
[{{< ai doi >}}](https://doi.org/10.15626/MP.2021.2803){target="_blank" style="color: inherit;"}
[{{< fa file-pdf >}}](https://raw.github.com/cartermaclab/carterlab-papers/main/2022_mckay-etal_meta-analytic-findings-of-the-self-controlled-motor-learning-literature-underpowered-biased-and-lacking-evidential-value.pdf){target="_blank" style="color: inherit;"}
[{{< fa brands github >}}](https://github.com/cartermaclab/proj_sc-meta-analysis){target="_blank" style="color: inherit;"}

- Lokesh R., Sullivan S., Calalo JA., Roth A., Swanik B., Carter MJ., & Cashaback JGA. (2022). Humans utilize sensory evidence of others’ intended action to make online decisions. *Scientific Reports*.  ---
[{{< ai doi >}}](https://doi.org/10.1038/s41598-022-12662-y){target="_blank" style="color: inherit;"}
[{{< fa file-pdf >}}](https://raw.github.com/cartermaclab/carterlab-papers/main/2022_lokesh-etal_humans-utilize-sensory-evidence-of-others-intended-action-to-make-online-decisions.pdf){target="_blank" style="color: inherit;"}
[{{< ai osf >}}](https://osf.io/bgf7t/){target="_blank" style="color: inherit;"}

- St. Germain L., Williams A., Balbaa N., Poskus A., Leshchyshen O., Lohse KR., & Carter MJ. (2022). Increased perceptions of autonomy through choice fail to enhance motor skill retention. *Journal of Experimental Psychology: Human Perception and Performance*. ---
[{{< ai doi >}}](){target="_blank" style="color: inherit;"}
[{{< fa file-pdf >}}](https://raw.github.com/cartermaclab/carterlab-papers/main/){target="_blank" style="color: inherit;"}
[{{< fa brands github >}}](){target="_blank" style="color: inherit;"}

## 2021

*Note. Parental leave January 2021 to August 2021*

- McKay B., Hussien J., Carter MJ., Yantha ZD., & Ste-Marie DM. (2021). Expecting to teach a novel golf putting task did not enhance retention performance: A replication attempt of Daou and colleagues. *Communications in Kinesiology*. ---
[{{< ai doi >}}](https://doi.org/10.51224/cik.v1i2.39){target="_blank" style="color: inherit;"}
[{{< fa file-pdf >}}](https://raw.github.com/cartermaclab/carterlab-papers/main/2021_mckay-etal_expecting-to-teach-a-novel-golf-putting-task-did-not-enhance-retention-performance-a-replication-attempt-of-daou-and-colleag.pdf){target="_blank" style="color: inherit;"}
[{{< fa brands github >}}](https://github.com/cartermaclab/expt_expect-to-teach){target="_blank" style="color: inherit;"}

## 2020

*Note. Lab shutdown from COVID-19 pandemic*

## 2019

- Ste-Marie DM., Carter MJ., & Yantha ZD. (2020). Self-controlled learning: Current findings, theoretical perspectives, and future directions. In N.J. Hodges & A.M. Williams (Eds.), *Skill Acquisition in Sport: Research, theory, and practice* (3rd ed.). Routledge. ---
[{{< ai doi >}}](https://doi.org/10.4324/9781351189750-7){target="_blank" style="color: inherit;"}
[{{< fa file-pdf >}}](https://raw.github.com/cartermaclab/carterlab-papers/main/2019_ste-marie-etal_self-controlled-learning.pdf){target="_blank" style="color: inherit;"}

- Barros JAC., Yantha ZD., Carter MJ., Hussien J., & Ste-Marie DM. (2019). Examining the impact of error estimation on the effects of self-controlled feedback. *Human Movement Science*. ---
[{{< ai doi >}}](https://doi.org/10.1016/j.humov.2018.12.002){target="_blank" style="color: inherit;"}
[{{< fa file-pdf >}}](https://raw.github.com/cartermaclab/carterlab-papers/main/2019_barros-etal_examining-the-impact-of-error-estimation-on-the-effects-of-self-controlled-feedback.pdf){target="_blank" style="color: inherit;"}

## 2018

- Carter MJ., Smith V., Carlsen AN., & Ste-Marie DM. (2018). Anodal transcranial direct current stimulation over the primary motor cortex does not enhance the learning benefits of self-controlled feedback schedules. *Psychological Research*. ---
[{{< ai doi >}}](https://doi.org/10.1007/s00426-017-0846-x){target="_blank" style="color: inherit;"}
[{{< fa file-pdf >}}](https://raw.github.com/cartermaclab/carterlab-papers/main/2018_carter-etal_anodal-transcranial-direct-current-stimulation-over-the-primary-motor-cortex-does-not-enhance-the-learning-benefits-of-self-c.pdf){target="_blank" style="color: inherit;"}

## 2017

- Carter MJ., & Ste-Marie DM. (2017). Not all choices are created equal: Task-relevant choices enhance motor learning compared to task-irrelevant choices. *Psychonomic Bulletin & Review*. ---
[{{< ai doi >}}](https://doi.org/10.3758/s13423-017-1250-7){target="_blank" style="color: inherit;"}
[{{< fa file-pdf >}}](https://raw.github.com/cartermaclab/carterlab-papers/main/2017_carter-ste-marie_not-all-choices-are-created-equal-task-relevant-choices-enhance-motor-learning-compared-to-task-irrelevant-choices.pdf){target="_blank" style="color: inherit;"}

- Carter MJ., & Ste-Marie DM. (2017). An interpolated activity during the knowledge-of-results delay interval eliminates the learning advantages of self-controlled feedback schedules. *Psychological Research*. ---
[{{< ai doi >}}](https://doi.org/10.1007/s00426-016-0757-2){target="_blank" style="color: inherit;"}
[{{< fa file-pdf >}}](https://raw.github.com/cartermaclab/carterlab-papers/main/2017_carter-ste-marie_an-interpolated-activity-during-the-knowledge-of-results-delay-interval-eliminates-the-learning-advantages-of-self-controlled.pdf){target="_blank" style="color: inherit;"}

- Carter MJ., & Maslovat D., & Carlsen AN. (2017). Intentional switches between coordination patterns are faster following anodal-tDCS applied over the supplementary motor area. *Brain Stimulation*. ---
[{{< ai doi >}}](https://doi.org/10.1016/j.brs.2016.11.002){target="_blank" style="color: inherit;"}
[{{< fa file-pdf >}}](https://raw.github.com/cartermaclab/carterlab-papers/main/2017_carter-etal_intentional-switches-between-coordination-patterns-are-faster-following-anodal-tdcs-applied-over-the-supplementary-motor-area.pdf){target="_blank" style="color: inherit;"}

- Maslovat D., Carter MJ., & Carlsen AN. (2017). Response preparation and execution during intentional bimanual pattern switching. *Journal of Neurophysiology*. ---
[{{< ai doi >}}](2017_maslovat-etal_response-preparation-and-execution-during-intentional-bimanual-pattern-switching.pdf){target="_blank" style="color: inherit;"}
[{{< fa file-pdf >}}](https://raw.github.com/cartermaclab/carterlab-papers/main/2017_maslovat-etal_response-preparation-and-execution-during-intentional-bimanual-pattern-switching.pdf){target="_blank" style="color: inherit;"}

## 2016

- Carter MJ., Smith V., & Ste-Marie DM. (2016). Judgments of learning are significantly higher following feedback on relatively good versus relatively poor trials despite no actual learning differences. *Human Movement Science*. ---
[{{< ai doi >}}](https://doi.org/10.1016/j.humov.2015.11.006){target="_blank" style="color: inherit;"}
[{{< fa file-pdf >}}](https://raw.github.com/cartermaclab/carterlab-papers/main/2016_carter-etal_judgments-of-learning-are-significantly-higher-following-feedback-on-relatively-good-versus-relatively-poor-trials-despite-no.pdf){target="_blank" style="color: inherit;"}

- Carter MJ., Rathwell S., & Ste-Marie DM. (2016). Motor skill retention is modulated by strategy choice during self-controlled knowledge of results schedules. *Journal of Motor Learning and Development*. ---
[{{< ai doi >}}](https://doi.org/10.1123/jmld.2015-0023){target="_blank" style="color: inherit;"}
[{{< fa file-pdf >}}](https://raw.github.com/cartermaclab/carterlab-papers/main/2016_carter-etal_motor-skill-retention-is-modulated-by-strategy-choice-during-self-controlled-knowledge-of-results-schedules.pdf){target="_blank" style="color: inherit;"}

- Martini R., Carter MJ., Yoxon E., Cumming J., & Ste-Marie DM. (2016). Development and validation of the Movement Imagery Questionnaire for Children (MIQ-C). *Psychology of Sport and Exercise*. ---
[{{< ai doi >}}](https://doi.org/10.1016/j.psychsport.2015.08.008){target="_blank" style="color: inherit;"}
[{{< fa file-pdf >}}](https://raw.github.com/cartermaclab/carterlab-papers/main/2016_martini-etal_development-and-validation-of-the-movement-imagery-questionnaire-for-children-miq-c.pdf){target="_blank" style="color: inherit;"}

- Patterson JT., Hart A., Hansen S., Carter MJ., & Ditor D. (2016). Measuring investment in learning: Can electrocardiogram provide an indication of cognitive effort during learning?. *Perceptual and Motor Skills*. ---
[{{< ai doi >}}](https://doi.org/10.1177/0031512516633348){target="_blank" style="color: inherit;"}
[{{< fa file-pdf >}}](https://raw.github.com/cartermaclab/carterlab-papers/main/2016_patterson-etal_measuring-investment-in-learning-can-electrocardiogram-provide-an-indication-of-cognitive-effort-during-learning.pdf){target="_blank" style="color: inherit;"}

- Ste-Marie DM., Carter MJ., Law B., Vertes K., & Smith V. (2016). Self-controlled learning benefits: exploring contributions of self-efficacy and intrinsic motivation via path analysis. *Journal of Sports Sciences*. ---
[{{< ai doi >}}](https://doi.org/10.1080/02640414.2015.1130236){target="_blank" style="color: inherit;"}
[{{< fa file-pdf >}}](https://raw.github.com/cartermaclab/carterlab-papers/main/2016_ste-marie-etal_self-controlled-learning-benefits-exploring-contributions-of-self-efficacy-and-intrinsic-motivation-via-path-analysis.pdf){target="_blank" style="color: inherit;"}

## 2015

- Carter MJ., Maslovat D., & Carlsen AN. (2015). Anodal transcranial direct current stimulation applied over the supplementary motor area delays spontaneous antiphase-to-in-phase transitions. *Journal of Neurophysiology*. ---
[{{< ai doi >}}](https://doi.org/10.1152/jn.00662.2014){target="_blank" style="color: inherit;"}
[{{< fa file-pdf >}}](https://raw.github.com/cartermaclab/carterlab-papers/main/2015_carter-etal_anodal-transcranial-direct-current-stimulation-applied-over-the-supplementary-motor-area-delays-spontaneous-antiphase-to-in-p.pdf){target="_blank" style="color: inherit;"}

- Maslovat D., Drummond NM., Carter MJ., & Carlsen AN. (2015). Reduced motor preparation during dual-task performance: Evidence from startle. *Experimental Brain Research*. ---
[{{< ai doi >}}](https://doi.org/10.1007/s00221-015-4340-7){target="_blank" style="color: inherit;"}
[{{< fa file-pdf >}}](https://raw.github.com/cartermaclab/carterlab-papers/main/2015_maslovat-etal_reduced-motor-preparation-during-dual-task-performance-evidence-from-startle.pdf){target="_blank" style="color: inherit;"}

- Maslovat D., Drummond NM., Carter MJ., & Carlsen AN. (2015). Startle activation is additive with voluntary cortical activation irrespective of stimulus modality. *Neuroscience Letters*. ---
[{{< ai doi >}}](https://doi.org/10.1016/j.neulet.2015.08.053){target="_blank" style="color: inherit;"}
[{{< fa file-pdf >}}](https://raw.github.com/cartermaclab/carterlab-papers/main/2015_maslovat-etal_startle-activation-is-additive-with-voluntary-cortical-activation-irrespective-of-stimulus-modality.pdf){target="_blank" style="color: inherit;"}

## 2014

- Carter MJ., Carlsen AN., & Ste-Marie DM. (2014). Self-controlled feedback is effective if it is based on the learner’s performance: a replication and extension of Chiviacowsky and Wulf (2005). *Frontiers in Psychology*. ---
[{{< ai doi >}}](https://doi.org/10.3389/fpsyg.2014.01325){target="_blank" style="color: inherit;"}
[{{< fa file-pdf >}}](https://raw.github.com/cartermaclab/carterlab-papers/main/2014_carter-etal_self-controlled-feedback-is-effective-if-it-is-based-on-the-learners-performance-a-replication-and-extension-of-chiviacow.pdf){target="_blank" style="color: inherit;"}

- Maslovat D., Carter MJ., Kennefick M., & Carlsen AN. (2014). Startle neural activity is additive with normal cortical initiation-related activation. *Neuroscience Letters*. ---
[{{< ai doi >}}](https://doi.org/10.1016/j.neulet.2013.11.009){target="_blank" style="color: inherit;"}
[{{< fa file-pdf >}}](https://raw.github.com/cartermaclab/carterlab-papers/main/2014_maslovat-etal_startle-neural-activity-is-additive-with-normal-cortical-initiation-related-activation.pdf){target="_blank" style="color: inherit;"}

## 2013

- Bajema MC., MacKinnon CD., Carter MJ., Kennefick M., Perlmutter S., & Carlsen AN. (2013). Pause time alters the preparation of two-component movements. *Experimental Brain Research*. ---
[{{< ai doi >}}](https://doi.org/10.1007/s00221-013-3670-6){target="_blank" style="color: inherit;"}
[{{< fa file-pdf >}}](https://raw.github.com/cartermaclab/carterlab-papers/main/2013_bajema-etal_pause-time-alters-the-preparation-of-two-component-movements.pdf){target="_blank" style="color: inherit;"}

- Patterson JT., Carter MJ., & Hansen S. (2013). Self-controlled KR schedules: Does repetition order matter?. *Human Movement Science*. ---
[{{< ai doi >}}](https://doi.org/10.1016/j.humov.2013.03.005){target="_blank" style="color: inherit;"}
[{{< fa file-pdf >}}](https://raw.github.com/cartermaclab/carterlab-papers/main/2013_patterson-etal_self-controlled-kr-schedules-does-repetition-order-matter.pdf){target="_blank" style="color: inherit;"}

## 2012

- Carter MJ. & Patterson JT. (2012). Self-controlled knowledge of results: Age-related differences in motor learning, strategies, and error detection. *Human Movement Science*. ---
[{{< ai doi >}}](https://doi.org/10.1016/j.humov.2012.07.008){target="_blank" style="color: inherit;"}
[{{< fa file-pdf >}}](https://raw.github.com/cartermaclab/carterlab-papers/main/2012_carter-patterson_self-controlled-knowledge-of-results-age-related-differences-in-motor-learning,-strategies,-and-error-detection.pdf){target="_blank" style="color: inherit;"}

## 2011

- Patterson JT., Carter MJ., & Sanli E. (2011). Decreasing the proportion of self-control trials during the acquisition period does not compromise the learning advantages in a self-controlled context. *Research Quarterly for Exercise and Sport*. ---
[{{< ai doi >}}](https://doi.org/10.1080/02701367.2011.10599799){target="_blank" style="color: inherit;"}
[{{< fa file-pdf >}}](https://raw.github.com/cartermaclab/carterlab-papers/main/2011_patterson-etal_decreasing-the-proportion-of-self-control-trials-during-the-acquisition-period-does-not-compromise-t.pdf){target="_blank" style="color: inherit;"}

## 2010

- Patterson JT. & Carter MJ. (2010). Learner regulated knowledge of results during the acquisition of multiple timing goals. *Human Movement Science*. ---
[{{< ai doi >}}](https://doi.org/10.1016/j.humov.2009.12.003){target="_blank" style="color: inherit;"}
[{{< fa file-pdf >}}](https://raw.github.com/cartermaclab/carterlab-papers/main/2010_patterson-carter_learner-regulated-knowledge-of-results-during-the-acquisition-of-multiple-timing-goals.pdf){target="_blank" style="color: inherit;"}

### 2025-01-17 team.qmd
site and layout updates

---
title: "Meet the team"
toc: false
listing:
  - id: senior
    contents: "team/senior/*.qmd"
    type: grid
    image-height: 225px
    grid-columns: 3
    fields: 
      - image
      - title
      - subtitle
    sort: sortby
    field-display-names: 
      started: "Started"
  - id: junior
    contents: "team/junior/*.qmd"
    type: grid
    image-height: 225px
    grid-columns: 3
    fields: 
      - image
      - title
      - subtitle
    sort: sortby
    field-display-names: 
      started: "Started"
---

## Senior members

:::{#senior}
:::

## Junior members

:::{#junior}
:::

@@

**Laura St. Germain**, Ph.D. Kinesiology (2018-23); *Research and Data Specialist at Sheridan College*  
**Mirette Mounir**, M.Sc. Kinesiology (2019-21); *Dentistry at Western University*  
**Rajbir Sihu**, M.Sc. Kinesiology (2019-21); *Dentistry at the University of Toronto*

>>>>

---
title: "Meet the team"
toc: false
---

<style>
.team-member {
  display: flex;
  align-items: center;
  padding: 20px; /* Add padding around each team member */
  border: 1px solid #ddd; /* Optional: Add a border for better visual separation */
  margin-bottom: 20px; /* Add space between each team member */
}

.team-img {
  margin-right: 20px;
  width: 175px; /* Set the desired width */
  height: 175px; /* Set the desired height */
  border-radius: 50%; /* Make the image rounded */
  object-fit: cover; /* Ensure the image covers the area */
}

.team-info {
  display: flex;
  flex-direction: column;
}
</style>

<div class="team-member">
  <img src="images/mike-carter.jpg" alt="images/mike-carter.jpg" class="team-img">
  <div class="team-info">
  <h4> Mike Carter, Ph.D. </h4>
  <p> Assistant Professor | Principal Investigator </p>
  <p> cartem11 [at] mcmaster [dot] ca </p>
  </div>
</div>

<div class="team-member">
  <img src="images/jack-tang.jpg" alt="images/jack-tang.jpg" class="team-img">
  <div class="team-info">
  <h4> Jiaqiao Tang, M.Sc.PT </h4>
  <p> Ph.D. Student </p>
  <p> tangj24 [at] mcmaster [dot] ca</p>
  </div>
</div>

<div class="team-member">
  <img src="images/mikayla-lalli.jpg" alt="images/mikayla-lalli.jpg" class="team-img">
  <div class="team-info">
  <h4> Mikayla Lalli, M.Sc. </h4>
  <p> Ph.D. Student </p>
  <p> lallim1 [at] mcmaster [dot] ca </p>
  </div>
</div>

<div class="team-member">
  <img src="images/nour-al-afif.jpg" alt="images/nour-al-afif.jpg" class="team-img">
  <div class="team-info">
  <h4> Nour Al Afif, M.Sc. </h4>
  <p> Ph.D. Student </p>
  <p> alafin1 [at] mcmaster [dot] ca </p>
  </div>
</div>

<div class="team-member">
  <img src="images/daniel-deletsu.jpg" alt="images/nour-alfif.jpg" class="team-img">
  <div class="team-info">
  <h4> Daniel Deletsu, B.Sc. </h4>
  <p> M.Sc. Student </p>
  <p> deletsud [at] mcmaster [dot] ca </p>
  </div>
</div>

@@

**Mikayla Lalli**, M.Sc. Kinesiology (2022-24); *Ph.D. student in the lab*.  
**Nour Al Afif**, M.Sc. Kinesiology (2022-24); *Ph.D. student in the lab*  
**Laura St. Germain**, Ph.D. Kinesiology (2018-23); *Research and Data Specialist at Sheridan College*  
**Mirette Mounir**, M.Sc. Kinesiology (2019-21); *Dentistry at Western University*  
**Rajbir Sihu**, M.Sc. Kinesiology (2019-21); *Dentistry at the University of Toronto*
